Modeling memory and taxis to analyze migrations

### 2021-01-21 code/StrategicVsTactical_PartI_v2.Rmd
fixed indices

---
title: "Modeling memory and taxis to analyze migrations"
author: "E. Gurarie, S. Potluri, B. Fagan, others"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
theme: cerulean
editor_options:
  chunk_output_type: console
---

@@

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Hybrid_PulsedResource_Sim, tau = tau)
plotYearList(Hybrid_PulsedResource_Sim, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)

>>>>

---
title: "Modeling memory and taxis to analyze migrations"
author: "E. Gurarie, S. Potluri, B. Fagan, others"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
theme: cerulean
editor_options:
  chunk_output_type: console
---

@@

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Hybrid_PulsedResource_Sim, tau = tau)
plotYearList(Hybrid_PulsedResource_Sim, tau = tau, 
             persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```
